Economic Evaluation of Mis-speficied Geographically Weighted Regression Models for Site-specific Nitrogen Management

### 2023-06-24 Writing/JAAEA/1stRoundRevision/reply_to_editor.rmd

Blur blur, . Your comments are in blue, and our responses are in black.

<span style = "color: blue;"> Based on the reviews and your email response, I have decided to give you the opportunity to revise the manuscript and respond to reviewer comments. One major point is that your true DGP assumed a quadratic plateau, but the estimated models use quadratic. This will lead the estimated models to give biased results. In your email response you indicate that you used quadratic plateau as the “true” functional form based on agronomy studies. If the dominant approach in recent literature is to use quadratic functions, then it does seem valuable to quantify the bias from using quadratic rather than quadratic plateau. Please document clearly in the manuscript that quadratic is the common practice (__point 1__). However, the title of your paper is about an economic evaluation of GWR analysis, and the choice of quadratic or quadratic-plateau is not an issue with GWR and this needs to be clear (__point 2__). Also reading through your discussion section, the implications are primarily framed about how GWR performed, but it might completely be an issue with functional form, but the current simulations don't inform us about the source of bias. Ideally, you would compare a GWR model that is quadratic with a GWR model that is quadratic-plateau functional form (__point 3__). </span>

Reply to <span style = "color: blue;"> __point 1__ </span>:

Actually, the dominant functional form used in the literature is quadratic-plateau for <span style = "color: red;"> non-</span>GWR (regualr parametric) regression because agronomists have long known that it better represents corn-nitrogen relationship. Application of GWR is very new to the field and GWR is not currently flexible in funcional form. There is no readily available statistical software or packages that lets researchers use the quadratic-plateau functionl form under the GWR framework. That is the primary reason that both Trevisan et al. (2021) and Rakshit et al. (2020) are using quadratic functional form. So, their choice of functional form is not coming from agronomic facts, rather from technical limitations. We are trying to point out this can be dangerous with GWR just like it is a problem for regular regression framework. So, our paper is imporatnt because many use quadratic-plateau in regular regression framework for corn-nitrogen yield response function estimation, but the GWR promoted by the two studies use quadratic just because it is hard to do so. We believe that this technical limitation is not trivial and would like to avoid practitioners or researcher believing GWR is better than it truly is. We further suggest that it is important to develope a statistical package that allows to model yield-input relationship more flexibly.

@@

Reply to <span style = "color: blue;"> __point 2__ </span>:

We fully agree with this point. We are assuming that readers know yield-nitrogen relationship is better represented by quadaratic-plateau and that point was kept implicit tghroughout the article. We made significant modifications to the manuscript so that we are not trying to blame GWR itself.

Reply to <span style = "color: blue;"> __point 3__ </span>:

This is a problem of our writing and we apologize for that. Our objective is not to evaluate the problem of GWR itself, rather the current practice of using GWR with quadratic form when the true underlying true relationship is quadratic-plateau as in Trevisan et al. (2021). But, we agree fully that it is interesting to see how GWR performs when the assumed funtional form in regression and true functional form in the data generating process are the same. However, please note that quadratic-plateu is a non-linear model and GWR with quadratic-plate cannot be estimated readily as of now.

@@

But, suppose we are interested in evaluating GWR itself. And, also suppose our DGP and the GWR DGP are very different even though they are in reality very similar as argued above. Even then, we can definitely criticize GWR by using our DGP. Nobody knows the true data generating process of OFPE in the real world. If we use the GWR DGP and find out that GWR performs well, then does that mean GWR performs well in the real world? No. It says that GWR performs well if the data generated in OFEP indeed follow GWR DGP, which of course may not be the true DGP in real world. If GWR does not perform well for a single DGP that is just as valid as GWR DGP, then that would mean we need to be careful applying GWR in the real world. This is not to say, GWR is always bad. But, it is enough to warrant researchers and practitioners that GWR <span style = "color: red;"> may </span> fail. If we show that GWR does not work well with "a" valid DGP, then it is enought to warn people about its potential danger.

<span style = "color: blue;"> In general, it is important in your paper to clarify how much of the bias you estimate is due to the functional form assumption versus the assumption about the DGP. Also, you need to more clearly defend the DGP you choose as the “true” DGP or compare results with alternative DGPs. It seems to me that you will need to rethink your simulations so that you can more clearly sort out the sources of bias. </span>

Reply:

It is not important in this paper to distinguish and isolate the sources of bias. Our interest is in showing the bias of using GWR with quadratic form (because of technical limitation) even though the underlying relatinship is quadratic-plateau (like corn-nitrogen) as done by Trevisan et al. (2021). It is actually impossible in our paper to isolate them and we are not interested in doing so either. Also, please note that functional form is part of DGP and indeed the most important part of a DGP. There is no such thing as isolating the source of bias of funcitonal form assumption and DGP assumption.

### 2023-06-24 Writing/manuscript_gwr.rmd
minor edits

**Abstract**: Geographically weighted regression (GWR) has been presented as a prominent tool to estimate site-specific yield response functions to derive site-specific input rate recommendations from data generated by on-farm precision experimentation (OFPE). However, the current application of GWR in this context assumes quadratic yield response function even though many of the yield-input relationships has been shown to be better represented by the quadratic-plateau functional form. This is due to lack of readily available methods and statistical packages that allow researchers to estimate non-linear model under the GWR framework, including quadratic-plateau. The key objective of this paper is to investigate the possibility of bias in estimating the economic value of site-specific recommendation maps based on GWR with quadratic functional form assumption when in reality the true underlying yield-input relationship is quadratic-plateau. We consider two sets of functional-form specifications used by two recent published studies of site-specific input management that apply GWR to data from OFPE. We show that both GWR approaches suffer significant positive bias, which can lead to large over-estimation of the economic value of applying GWR methods. We reveal that in many circumstances using GWR is far less profitable than claimed by previous studies, which provides a necessary cautionary message to researchers who might otherwise “over-sell” to other researchers the value of using GWR methods in empirical work involving the estimation of site-specific input management. We encourage the statistical community to extend the current GWR capability by allowing researchers to model yield-input response more flexibly than currently possible.

@@

We found that the benefit of VRA over URA is rather small irrespective of the specification used, averaging only about \$5 ha$^{-1}$. More important, both specifications by trevisan2021spatial and rakshit2020 tend to significantly over-estimate the economic value of VRA based on GWR. Their assumption of quadratic funcitonal form is one of the main culplits. When quadratic functional form is assumed, over-application of nitrogen is modeled to result in large economic loss due to yield loss when in reality over-application of nitrogen is not associated with any yield loss when the true yield-response function is quadratic-plateau. Our results suggest that the prospects of using GWR to generate site-specific input recommendations are bleaker than stated in @trevisan2021spatial. It is important to develop GWR with more flexible functional forms than currently possible if precision agriculture practitioner is interested in using GWR as one of the tools to estimate site-specific input use recommendation.

@@

Finally, it would be interesting to examine the pure performance of GWR. The objective of this article was to evaluate GWR with quadratic functional form when the true yield-input relationship is quadratic-plateau. Therefore, we evaluated GWR when model is misspecified in a particular manner. Once, GWR with quadratic-plateau model is developed, it would be interesting to see how it performs when the true yield response to input is quadratic-plateau. In this case, there is no functional form misspecification and the pure ability of GWR can be isolated.

>>>>

**Abstract**: Geographically weighted regression (GWR) has been presented as a prominent tool to estimate site-specific yield response functions to derive site-specific input rate recommendations from data generated by on-farm precision experimentation (OFPE). However, the current application of GWR in this context assumes quadratic yield response function even though many of the yield-input relationships has been shown to be better represented by the quadratic-plateau functional form. This is due to lack of readily available methods and statistical packages that allow researchers to estimate non-linear model under the GWR framework, including quadratic-plateau. The key objective of this paper is to investigate the possibility of bias in estimating the economic value of site-specific recommendation maps based on GWR with quadratic functional form assumption when in reality the true underlying yield-input relationship is quadratic-plateau. We consider two sets of functional-form specifications used by two recent published studies of site-specific input management that apply GWR to data from OFPE. We show that both GWR approaches suffer significant positive bias, which can lead to large over-estimation of the economic value of applying GWR methods. We reveal that in many circumstances using GWR is far less profitable than claimed by previous studies, which provides a necessary cautionary message to researchers who might otherwise "over-sell" to other researchers the value of using GWR methods in empirical work involving the estimation of site-specific input management. We encourage the statistical community to extend the current GWR capability by allowing researchers to model yield-input response more flexibly than currently possible.

@@

We found that the benefit of VRA over URA is rather small irrespective of the specification used, averaging only about \$5 ha$^{-1}$. More important, both specifications by trevisan2021spatial and rakshit2020 tend to significantly over-estimate the economic value of VRA based on GWR. Their assumption of quadratic functional form is one of the main culprits. When quadratic functional form is assumed, over-application of nitrogen is modeled to result in large economic loss due to yield loss when in reality over-application of nitrogen is not associated with any yield loss when the true yield-response function is quadratic-plateau. Our results suggest that the prospects of using GWR to generate site-specific input recommendations are bleaker than stated in @trevisan2021spatial. It is important to develop GWR with more flexible functional forms than currently possible if precision agriculture practitioner is interested in using GWR as one of the tools to estimate site-specific input use recommendation.

@@

Finally, it would be interesting to examine the pure performance of GWR. The objective of this article was to evaluate GWR with quadratic functional form when the true yield-input relationship is quadratic-plateau. Therefore, we evaluated GWR when model is mis-specified in a particular manner. Once, GWR with quadratic-plateau model is developed, it would be interesting to see how it performs when the true yield response to input is quadratic-plateau. In this case, there is no functional form mis-specification and the pure ability of GWR can be isolated.
